---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(tidyverse)
library(stringr)
```

```{r}
df_ks <- read.csv("C:/Users/Aldo Gadra/Documents/Data overview/Data project/Data/most_backed.csv")
```

goal_reached merupakan percentage total pledge dengan goal 
```{r}
df_ks <- df_ks %>%
mutate(goal_reached = (amt.pledged / goal) * 100)
```

mutate category
```{r}
df_ks1 <- df_ks %>%
  mutate(pleged_level = factor(ifelse(goal_reached>1000,"extremely high",
                                "achieved")))
```

mutate average spending
```{r}
df_ks1 <- df_ks1 %>%
  mutate(avg_pledge = amt.pledged/num.backers)
```

Hitung jumlah tier
Convert ot list
Eliminating {} - Terakhir di sini
```{r}
df_ks1 <- df_ks1 %>% mutate(pledge.tier = str_replace_all(pledge.tier, "\\*|\\[|\\]", ""))
```

Count num
```{r}
df_ks1 <- df_ks1 %>%
  mutate(num.tiers = lengths(gregexpr(",", pledge.tier)) + 1)
```

Visualisasi dan EDA 
1. Checkcing missing values 
```{r}
df_ks1 %>% is.na() %>% colSums()
```
```{r}
df_ks1 = df_ks1[complete.cases(df_ks1),]
```

2. Missing Value 
```{r}
# Banyaknya sample original
df_ks1 %>% nrow()
```
Disini ada jumlah row unik (distinct) kurang dari total jumlah baris -> ada dulpikat
```{r}
# Banyaknya sample setelah membuang filter
df_ks1 %>% distinct(blurb) %>% nrow()
```
```{r}
df_ks1 %>% 
  group_by(blurb) %>% 
  filter(n()>1) %>% 
  arrange(blurb) 
```
Dropping duplicated category column 
```{r}
duplicated_ks = df_ks1 %>% 
  group_by(blurb) %>% 
  filter(n()>1) %>% 
  distinct(blurb) %>% 
  pull(blurb)

df_ks1 = filter(df_ks1,! blurb %in% duplicated_ks)
```

```{r}
unique(df_ks1[c("category")])
```

3. EDA 
Random visualization (game related)
```{r}
df_ks1 %>%
  filter(category %in% c("Games", "Gaming Hardware", "Video Games", "Tabletop Games")) %>%
  ggplot() + 
  geom_boxplot(aes(x =  category, y = num.backers, fill= category)) +
  theme(legend.position="none") +
  coord_flip() 
```

10 Jensi projcect dengan paling Pendaaan (pledged)
```{r}
df_ks1 %>%
  group_by(category) %>%
  summarise(n=sum(amt.pledged, na.rm=TRUE)) %>%
  arrange(desc(n))%>%
  head(10) %>%
  ggplot(aes(x= reorder(category,n), y = n, fill=category)) + 
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = scales::comma)
```
Number of Projects
```{r}
df_ks2 %>%
  filter(pleged_level == "achieved")  %>%
  ggplot(aes(x= category)) + 
  geom_bar() +
  coord_flip() 
```
Price boxplot
```{r}
df_ks2 %>%
  filter(pleged_level == "achieved") %>%
  ggplot() + 
  geom_boxplot(aes(x =  category, y = goal, fill= category)) +
  coord_flip()
```
Number of backers
```{r}
df_ks2 %>%
  filter(pleged_level == "achieved") %>%
  ggplot() + 
  geom_boxplot(aes(x =  category, y = num.backers, fill= category)) +
  coord_flip()
```


```{r}
df_ks2 %>%
  filter(pleged_level == "achieved") %>%
  ggplot() + 
  geom_boxplot(aes(x =  category, y = goal_reached, fill= category)) +
  theme(legend.position="none") +
  coord_flip() 
```

```{r}
df_ks2 %>%
  filter(pleged_level == "achieved") %>%
  ggplot() + 
  geom_boxplot(aes(x =  category, y = avg_pledge, fill= category)) +
  theme(legend.position="none") +
  coord_flip() 
```
```{r}
df_ks2 %>%
  filter(pleged_level == "achieved") %>%
  ggplot() + 
  geom_boxplot(aes(x =  category, y = avg_pledge, fill= category)) +
  theme(legend.position="none") +
  coord_flip() 
```


```{r}
df_ks1 %>%
  filter(category %in% c("Games", "Gaming Hardware", "Video Games", "Tabletop Games") & pleged_level == "extremely high") %>%
  ggplot(aes(x =  num.backers, y = goal_reached)) +
  geom_point(aes(colour= category)) +
  geom_text(aes(label = by), check_overlap = TRUE)

```
 
```{r}
df_ks1 %>%
  filter(category %in% c("Games", "Gaming Hardware", "Video Games", "Tabletop Games") & pleged_level == "achieved") %>%
  ggplot(aes(x =  avg_pledge, y = goal_reached)) +
  geom_point(aes(colour= category)) +
  geom_smooth(aes(colour= category),method = 'lm', se=FALSE)
```
# An exploration through the backers 
```{r}
df_ks2 %>%
  filter(category %in% c("Product Design", "Tabletop Games", "Technology") & 
  (pleged_level == "achieved")) %>%
  ggplot(aes(x =  num.backers, y = goal_reached)) +
  geom_point(aes(colour= category)) +
  geom_smooth(aes(colour= category),method = 'lm', se=FALSE)
```

```{r}
df_ks2 %>%
  filter(category %in% c("Product Design", "Tabletop Games", "Technology") & 
  (pleged_level == "achieved")) %>%
  ggplot(aes(x =  num.backers, y = amt.pledged)) +
  geom_point(aes(colour= category)) +
  geom_smooth(aes(colour= category),method = 'lm', se=FALSE)
```

```{r}
df_ks2 %>%
  filter(category %in% c("Product Design", "Tabletop Games", "Technology", "Gadgets") &     pleged_level == "achieved") %>%
  ggplot(aes(x =num.backers, y = goal)) +
  geom_point(aes(colour= category)) +
  geom_smooth(aes(colour= category),method = 'lm', se=FALSE)
```


Correlation [caetgorical]
Using Differecnet Data 
```{r}
library(caTools)
set.seed(123)
sample_ks <- sample.split(df_ks2$admit_prob, SplitRatio = .80)
train_ks <- subset(data, sample == TRUE)
test_ks <- subset(data, sample == FALSE)
```


